SoK: Application Attack Defenses (in Question)

### 2014-10-07 docs/questioning.tex
some more on methodology
typo

The prevalence is the prior probability that an event is an attack,
based on our understanding of the volume and frequency of attacks; the
\textsc{ppv} and \textsc{npv} are the revised estimates of the
probability based on the results of the detection
mechanism~\cite{altman1994}.

In what follows we evaluate published research in attack detection
mechanism based on the following:
\begin{itemize}
\item Reporting of values for True Positives ($a$), False Positives
  ($b$), False Negatives ($c$), True Negatives ($d$), on test
  environments.
\item Reporting of values for True Positives ($A$), False Positives
  ($B$), False Negatives ($C$), True Negatives ($D$), on the
  performance of the mechanism on environment with real attack
  profiles.
\end{itemize}

>>>>

The prevalence is the prior probability that an event is an attack,
based on our understanding of the volume and frequency of attacks; the
\textsc{ppv} and \textsc{npv} are the revised estimates of the
probability based on the results of the detection
mechanism~\cite{altman1994}. The lower the prevalence of an attack,
the more confident we can be that a negative test result indicates
that no attack has taken place and the less sure we can be that a
positive test result indicates a real attack.

In what follows we evaluate published research in attack detection
mechanism based on the following:
\begin{itemize}
\item Reporting of values for True Positives ($a$), False Positives
  ($b$), False Negatives ($c$), True Negatives ($d$), on test
  environments.
\item Reporting of values for True Positives ($A$), False Positives
  ($B$), False Negatives ($C$), True Negatives ($D$), on the
  performance of the mechanism on environments with real attack
  profiles.
\end{itemize}
